Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-01-28 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
HS: preliminary plot

\subsection{dynamical Chern-Simons}

@@

\begin{table*}[th]
\begin{tabular}{c | c c c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
\hline
sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots & \cite{Pierini:2021jxd} & $\alpha^{1/2}_{\rm GB} \ell \leqslant 1.7$~km~\cite{Perkins:2021mhb} & \dots \\
dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam} & $\alpha^{1/2}_{\rm CS} \ell \leqslant 8.5$~km~\cite{Silva:2020acr} & \dots \\
cEFTofGR & 4 & $-0.3680$ / $-0.5131$  & 1.9242 / 1.7000 & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
\hline
\hline
\end{tabular}
\caption{Summary of the quasinormal modes calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
references from which we used the results from and the current best constraint
(if applicable).
%
In the entries for cEFTofGR, the first entries in the $\delta
\omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
\emph{only parity-even correnctions} and the second entries by considering
\emph{only parity-odd corrections}. In these cases, the dimensionless parameters
$\lambda_{\rm e,o}$ are degenerate with the lengthscale $\ell$.
%
\hs{Add a column with the constraint (if any) that we placed.}
\hs{TODO: add which runs are done and which need to be done.}
}
\label{tab:ref_theories_qnms}
\end{table*}

@@

@@

%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%
We thank Emanuele~Berti, Andrea~Maselli, Caio~F.~B.~Macedo, Deyan~Mihailov, and
Serguei~Ossokine for discussions.
%
We thank the computational resources provided by the AEI, specifically the
{\sc Hypatia} cluster.
%
The authors would like to thank everyone at the frontline of the Covid-19
pandemic.
%%%%%%%%%%%%%%%%%

% \bibliographystyle{apsrev}
\bibliography{biblio}

>>>>

\subsection{dynamical Chern-Simons gravity}

@@

\begin{table*}[th]
\begin{tabular}{c | c c c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
\hline
sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots &  \cite{Pierini:2021jxd} & $\ell_{\rm GB} \leqslant 1.7$~km~\cite{Perkins:2021mhb} & \dots \\
dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam}   & $\ell_{\rm CS} \leqslant 8.5$~km~\cite{Silva:2020acr}   & \dots \\
cEFTofGR & 4 & $-0.3680$ / $-0.5131$  & 1.9242 / 1.7000 & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
\hline
\hline
\end{tabular}
\caption{Summary of the quasinormal modes calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
references from which we used the results from and the current best constraint
(if applicable).
%
In the entries for cEFTofGR, the first entries in the $\delta
\omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
\emph{only parity-even correnctions} and the second entries by considering
\emph{only parity-odd corrections}. In these cases, the dimensionless parameters
$\lambda_{\rm e,o}$ are degenerate with the lengthscale $\ell$.
%
\hs{Add a column with the constraint (if any) that we placed.}
\hs{TODO: add which runs are done and which need to be done.}
}
\label{tab:ref_theories_qnms}
\end{table*}

@@

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/dcs_GW200129.pdf}
\caption{Preliminary plot.}
\label{fig:dCS_bounds}
\end{figure}

@@

%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%
We thank Emanuele~Berti, Andrea~Maselli, Caio~F.~B.~Macedo, Deyan~Mihaylov, and
Serguei~Ossokine for discussions.
%
We thank the computational resources provided by the AEI, specifically the
{\sc Hypatia} cluster and Steffen Grunewald for assistance.
%
The authors would like to thank everyone at the frontline of the Covid-19
pandemic.
%%%%%%%%%%%%%%%%%

% \bibliographystyle{apsrev}
\bibliography{paper_alt_theor_bounds}
